Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-15 paper/paper.tex
more consistent terminology

\begin{abstract}
Subgraph isomorphism is a computationally challenging problem with important practical
applications, for example in computer vision, biochemistry, and model checking. There are a number
of state-of-the-art algorithms for solving the problem, each of which has its own performance
characteristics. As with many other hard problems, the single best choice of algorithm overall is
rarely the best algorithm on an instance-by-instance. We develop a portfolio approach which leverages
novel features to characterise subgraph isomorphism problems to dynamically decide which algorithm
to use on a per-instance basis. We demonstrate substantial performance improvements on a large set
of hard benchmark problems. In addition, we show how algorithm selection models can be leveraged to
gain new insights into what affects the performance of an algorithm.
\end{abstract}

@@

Figure~\ref{fig:portfolio-ecdf} shows the number of solved instances over time
for the individual solvers, the virtual best solver, and the \LLAMA algorithm
selection approach. The performance of \VFtwo is far behind all other solvers.
The portfolio does not perform well for instances that can be solved quickly
because of the overhead incurred through feature computation. As the instances
become more difficult to solve, its performance improves.

@@

Figure~\ref{fig:portfolio-ecdf-full} shows the number of solved instances over
time for the algorithm selection system including
\IncompleteLAD and \VFtwo presolving on the full set of instances. Note that for
very easy instances, we are better than the virtual best solver because
\IncompleteLAD is not included in our portfolio. The performance on small
instances is much better than the \LLAMA selector alone (cf.\
Figure~\ref{fig:portfolio-ecdf}) and the region where the portfolio performs
worse than the individual solvers is now limited to approximately $10^2$ to
$10^5$ milliseconds.

@@

We demonstrated that our portfolio achieves substantial performance improvements
over the single algorithm that has the best performance on our benchmark set. We
showed that combining a portfolio approach with a novel incomplete variant of
\LAD that is able to detect inconsistencies and a presolver boosts performance
even further.

>>>>

\begin{abstract}
Subgraph isomorphism is a computationally challenging problem with important practical
applications, for example in computer vision, biochemistry, and model checking. There are a number
of state-of-the-art algorithms for solving the problem, each of which has its own performance
characteristics. As with many other hard problems, the single best choice of algorithm overall is
rarely the best algorithm on an instance-by-instance. We develop an algorithm
selection approach which leverages
novel features to characterise subgraph isomorphism problems to dynamically decide which algorithm
to use on a per-instance basis. We demonstrate substantial performance improvements on a large set
of hard benchmark problems. In addition, we show how algorithm selection models can be leveraged to
gain new insights into what affects the performance of an algorithm.
\end{abstract}

@@

Figure~\ref{fig:portfolio-ecdf} shows the number of solved instances over time
for the individual solvers, the virtual best solver, and the \LLAMA algorithm
selection approach. The performance of \VFtwo is far behind all other solvers.
The algorithm selection model does not perform well for instances that can be
solved quickly because of the overhead incurred through feature computation. As
the instances become more difficult to solve, its performance improves.

@@

Figure~\ref{fig:portfolio-ecdf-full} shows the number of solved instances over
time for the algorithm selection system including
\IncompleteLAD and \VFtwo presolving on the full set of instances. Note that for
very easy instances, we are better than the virtual best solver because
\IncompleteLAD is not included in our portfolio. The performance on small
instances is much better than the \LLAMA selector alone (cf.\
Figure~\ref{fig:portfolio-ecdf}) and the region where \LLAMA performs
worse than the individual solvers is now limited to approximately $10^2$ to
$10^5$ milliseconds.

@@

We demonstrated that our algorithm selection approach achieves substantial
performance improvements over the single algorithm that has the best performance
on our benchmark set. We showed that combining an algorithm selection approach
with a novel incomplete variant of \LAD that is able to detect inconsistencies
and a presolver boosts performance even further.
